\textls[-0]{\thetitle}

### 2023-03-04 metatheory-condensed.tex

In dependent type system, types are treated as terms, and should have a type. % Reviewer A : Why is W(t) a term and not a type?
We use Tarski-style universes~\cite{hofmann1997syntax}: every type has a \emph{code}, inhabits in a universe~$\cU$,
with $\El{t}$ decoding~$t$ (rule \ruleref{ty/el})
and $\codety{T}$ encoding type~$T$ (rule \ruleref{tm/c}).
MLTT has an infinite hierarchy of universes;
we omit universe levels in the presentation for conciseness.

@@

W-types~\cite{martin1984intuitionistic} are a succinct way to model
inductive types in MLTT.
Together with the identity type $\TyId{\cDot}{\cDot}$, they can express a
whole host of inductive types~\cite{hugunin2021not}.
%
A constructor is given by a pair of types
$\goodType{\Gm}{A}{}$ and $\goodType{\Gm,A}{B}{}$ (rule \ruleref{wsig/add}):
given two arguments $\goodTerm{\Gm}{t_1}{A}$ and
$\goodTerm{\Gm,\sub{B}{\SubstExt{\SubstWeak{0}}{t_1}}}{t_2}{T}$,
we can constructs a term $\Wsup{\wsig}{t_1}{t_2}$ of type~$T$ (rule \ruleref{tm/wsup}). % Reviewer B: Line 666
As the rules suggest, our formulation additionally supports
\emph{W-type signatures}.
A well formed W-type signature \goodWSig{\Gm}{\wsig}{n} is
composed of $n$ pairs of types, each of which represents a constructor
(rules \ruleref{wsig/empty} and \ruleref{wsig/add}),
with $\wsigproj{i}{1}{\wsig}$ and $\wsigproj{i}{2}{\wsig}$ giving the
$i$-th pair in~$\wsig$, and $\wcode{\wsig}$ giving the code of the W-type (\ruleref{tm/w}).

>>>>

In dependent type system, types are treated as terms, and should have a type. \rA{Why is W(t) a term and not a type?}\EDJreply{changed, please review.}
We use Tarski-style universes~\cite{hofmann1997syntax}: every type has a \emph{code}, inhabits in a universe~$\cU$,
with $\El{t}$ decoding~$t$ (rule \ruleref{ty/el})
and $\codety{T}$ encoding type~$T$ (rule \ruleref{tm/c}).
MLTT has an infinite hierarchy of universes;
we omit universe levels in the presentation for conciseness.

@@

W-types~\cite{martin1984intuitionistic} are a succinct way to model
inductive types in MLTT.
Together with the identity type $\TyId{\cDot}{\cDot}$, they can express a
whole host of inductive types~\cite{hugunin2021not}.
%
A constructor is given by a pair of types
$\goodType{\Gm}{A}{}$ and $\goodType{\Gm,A}{B}{}$ (rule \ruleref{wsig/add}):
given two arguments $\goodTerm{\Gm}{t_1}{A}$ and
$\goodTerm{\Gm,\sub{B}{\SubstExt{\SubstWeak{0}}{t_1}}}{t_2}{T}$,
we can constructs a term $\Wsup{\wsig}{t_1}{t_2}$ of type~$T$ (rule \ruleref{tm/wsup}). \rB{for readability please add text between "T," and "Wsup"}\EDJreply{changed, please review}
As the rules suggest, our formulation additionally supports
\emph{W-type signatures}.
A well formed W-type signature \goodWSig{\Gm}{\wsig}{n} is
composed of $n$ pairs of types, each of which represents a constructor
(rules \ruleref{wsig/empty} and \ruleref{wsig/add}),
with $\wsigproj{i}{1}{\wsig}$ and $\wsigproj{i}{2}{\wsig}$ giving the
$i$-th pair in~$\wsig$, and $\wcode{\wsig}$ giving the code of the W-type (\ruleref{tm/w}).
